A Bayesian networks approach to infer social changes in burials in northeastern Taiwan during the European colonization period

### 2021-05-08 analysis/paper/paper.Rmd
Clarify the use of priors

<!-- add text about prior setting and anthropological assumptions of our prior values --> 
Normal distributions for the priors are typical in network analysis studies that assume networks to have low density and high transitivity, as are commonly found in the real world [@Caimo2017]. Thus, we specified the prior of the edge density parameter to low for both network models, following a normal distribution with mean at `r priors$mean_same[1]`, and standard deviations at `r priors$sigma_same[1]` (i.e (N(`r priors$mean_same[1]`, `r priors$sigma_same[1]`))). For covariates about biological features, such as age, sex, we specified a vague prior (N(`r priors$mean_same[2]`, `r priors$sigma_same[2]`)) for both models to explore their effects. For physical distance between burials, we also set a vague prior (N(`r priors$mean_same[8]`, `r priors$sigma_same[8]`)) to explore whether there is kinship-based proximity, e.g. stronger correlations for shorter distances. To evaluate our anthropological model of increased social inequality over time based on assumptions of corporate-network strategies [@Drennan2010; @Feinman2000], we incorporated different prior information for the network variables that are meaningful for social inequality, especially for transitivity and centralization. We set the priors to higher transitivity (N(`r priors$pre_prior_mean[6]`, `r priors$pre_prior_sigma[6]`)), lower centralization (N(`r priors$pre_prior_mean[7]`, `r priors$pre_prior_sigma[7]`)), and higher covariate effect of ritual activity (N(`r priors$pre_prior_mean[4]`, `r priors$pre_prior_sigma[4]`)) for the network before European contact to indicate less social differentiation and emphasize the ritual element shared in corporate groups. Conversely, we set the priors for the network after European arrival to lower transitivity (N(`r priors$post_prior_mean[6]`, `r priors$post_prior_sigma[6]`)), higher centralization (N(`r priors$post_prior_mean[7]`, `r priors$post_prior_sigma[7]`)), and a higher covariate effect for burial values (N(`r priors$post_prior_mean[5]`, `r priors$post_prior_sigma[5]`)) to model an increased social differentiation after European contact.

>>>>

<!-- add text about prior setting and anthropological assumptions of our prior values --> 
Priors are the distinctive aspect of Bayesian methods to estimate population by combining one's beliefs with data [@Gill2014]. Normal distribution N($\mu$, $\sigma^2$), where $\mu$ is mean and $\sigma^2$ is standard deviation, is typical for prior specification to model network parameters because it is sensible and convenient, allowing adjustments for a wide range of prior information [@Caimo2017; @Normand1992]. The larger the mean of the prior distribution, the more positive effect of that parameter on network formation. For standard deviation, if it is larger, it presents a relatively vague prior enabling comparison between variables that we do not have specific assumptions. Since low density is commonly found in the real world [@Caimo2017], we specified the prior of the edge density parameter to low for both network models, following a normal distribution with mean at `r priors$mean_same[1]`, and standard deviations at `r priors$sigma_same[1]` (i.e (N(`r priors$mean_same[1]`, `r priors$sigma_same[1]`))).

To evaluate our anthropological model of increased social inequality over time based on assumptions of corporate-network strategies [@Drennan2010; @Feinman2000], we specify priors that are meaningful for social inequality, especially for the variables of transitivity and centralization. We set the priors to higher transitivity (N(`r priors$pre_prior_mean[6]`, `r priors$pre_prior_sigma[6]`)), lower centralization (N(`r priors$pre_prior_mean[7]`, `r priors$pre_prior_sigma[7]`)), and higher covariate effect of ritual activity (N(`r priors$pre_prior_mean[4]`, `r priors$pre_prior_sigma[4]`)) for the network before European contact to indicate less social differentiation and emphasize the ritual element shared in corporate groups. Conversely, we set the priors for the network after European arrival to lower transitivity (N(`r priors$post_prior_mean[6]`, `r priors$post_prior_sigma[6]`)), higher centralization (N(`r priors$post_prior_mean[7]`, `r priors$post_prior_sigma[7]`)), and a higher covariate effect for burial values (N(`r priors$post_prior_mean[5]`, `r priors$post_prior_sigma[5]`)) to model an increased social differentiation after European contact. For covariates about biological features, such as age, sex, we specified a vague prior (N(`r priors$mean_same[2]`, `r priors$sigma_same[2]`)) for both models to explore their effects. For physical distance between burials, we also set a vague prior (N(`r priors$mean_same[8]`, `r priors$sigma_same[8]`)) to explore whether there is kinship-based proximity, e.g. stronger correlations for shorter distances.
